---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(tidyr)
library(ggplot2)
library(dplyr)
```

```{r}
library(RColorBrewer)
```


```{r}
games_sales_full <- read_csv("games_sales_full_cleaned.csv")
```


```{r}
games_sales_full_total <- read_csv("games_sales_full_total_cleaned.csv")
```

Due to the size of the file I will focuson on the top sales for analysis
```{r}
games_sales_full_total_top_200 <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  slice(1:200)
games_sales_full_total_top_200
```

```{r}
games_sales_full_total_top_50 <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  slice(1:50)
games_sales_full_total_top_50
```


```{r}
summary(games_sales_full_total)
```

##### 1. Use graph
```{r}
games_sales_full_total_top_200 %>%
  group_by(genre) %>% 
  ggplot(aes(x = genre, fill = genre) ) +
  geom_bar() +
  labs(title = "Games count by genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Genre") +
  coord_flip()

```

```{r}
games_sales_full_total_top_200 %>%
  group_by(genre) %>% 
  ggplot(aes(x = genre, fill = genre) ) +
  geom_bar() +
  theme(legend.position="none") +
  labs(title = "Games count by genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Genre") +
  coord_flip()
ggsave("genre_count.png")
```



##### 2. Use graph ???? 
```{r}
games_sales_full_total_top_200 %>% 
  group_by(publisher) %>% 
  ggplot(aes(x = genre, fill = publisher) ) +
  geom_bar() +
  labs(title = "Games count by publisher and genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Publisher") +
  coord_flip()
```

##### 
```{r}
games_sales_full_total_top_200 %>% 
  group_by(developer) %>% 
  ggplot(aes(x = genre, fill = developer) ) +
  geom_bar() +
  labs(title = "Games count by developer and genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Developer") +
  coord_flip()

```

```{r}
games_sales_full_total_top <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  slice(1:50)
games_sales_full_total_top

```

##### 3. Use graph
```{r}
games_sales_full_total_top %>% 
  group_by(developer) %>% 
  ggplot(aes(x = genre, fill = developer) ) +
  geom_bar() +
  labs(title = "Games count by developer and genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Developer") +
  coord_flip()
ggsave("genre_developer.png")
```

########## 

##### 3.5 Use graph - Genre and Dev flipped 
```{r}
games_sales_full_total_top %>% 
  group_by(developer) %>% 
  ggplot(aes(x = developer, fill = genre) ) +
  geom_bar() +
  labs(title = "Games count by developer and genre") +
  labs(x = "Developer") +
  labs(y = "Number of Games") +
  labs(fill = "Genre") +
  coord_flip()
ggsave("developer_genre.png")
```



```{r}
games_sales_full_total_top_games <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  slice(1:20)
games_sales_full_total_top_games
```

##### 4. Use graph
```{r}
games_sales_full_total_top_games %>% 
  group_by(name) %>% 
  ggplot(aes(x = name, y = total_global_sales, fill = name)) +
  geom_col() +
  labs(title = "Top 20 games sales by name") +
  labs(x = "Name") +
  labs(y = "Top 20 global sales") +
  labs(fill = "Name") +
  coord_flip()
ggsave("top20_games.png")
```

```{r}
games_sales_full_total_top_games %>% 
  group_by(name) %>% 
  ggplot(aes(x = name, y = total_global_sales, fill = name)) +
  geom_col() +
  theme(legend.position="none") +
  labs(title = "Top 20 games sales by name") +
  labs(x = "Name") +
  labs(y = "Top 20 global sales") +
  labs(fill = "Name") +
  coord_flip()
ggsave("top20_games.png")

```

```{r}
games_sales_full_total_top_games_genre <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  slice(1:40)
games_sales_full_total_top_games_genre
```

```{r}
games_sales_full_total_top_games_genre_select <- games_sales_full_total %>%
  arrange(desc(total_global_sales)) %>%
  select(rank, name, genre, platform, total_global_sales) %>%
  slice(1:50)
games_sales_full_total_top_games_genre_select
```

```{r}
games_sales_full_total_top_games_genre %>% 
  group_by(name) %>% 
  ggplot(aes(x = name, y = total_global_sales, fill = genre)) +
  geom_col() +
  labs(title = "Top 40 games sales by name and genre") +
  labs(x = "Name") +
  labs(y = "Top 40 global sales") +
  labs(fill = "Genre") +
  coord_flip()
ggsave("top40_games_name_genre.png")

```

k-means
```{r}
#games_sales_full_total_top_games_genre %>% 
 # unnest(cols = c(augmented)) %>%
  #filter(k == 2) %>%
# ggplot(aes(x = murder, y = assault, colour = .cluster, label = .rownames)) +
 # geom_point(aes(color = .cluster)) +
 # geom_text(hjust = 0, vjust = - 0.5, size = 3)
```



##### 5. Use graph
```{r}
games_sales_full_total_top_200 %>% 
  group_by(developer) %>% 
  ggplot(aes(x = genre, fill = platform)) +
  geom_bar() +
  labs(title = "Games count by platform and genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Platform") +
  coord_flip()
ggsave("count_platform_genre.png")
```


##### 6. Use graph - graph 5. swapped use 5 OR 6
```{r}
games_sales_full_total_top_200 %>% 
  group_by(developer) %>% 
  ggplot(aes(x = platform, fill = genre)) +
  geom_bar() +
  labs(title = "Games count by genre and platform") +
  labs(x = "Platform") +
  labs(y = "Number of Games") +
  labs(fill = "Genre") +
  coord_flip()
ggsave("count_genre_platform.png")
```

Already used as graph 1
```{r}
games_sales_full_total_top_200 %>% 
  group_by(genre) %>% 
  ggplot(aes(x = genre, fill = genre)) +
  geom_bar() +
  labs(title = "Games count by genre") +
  labs(x = "Genre") +
  labs(y = "Number of Games") +
  labs(fill = "Genre") +
  coord_flip()
ggsave("genre_count.png")
```

Games by platform
```{r}
games_sales_full_total_top_200 %>% 
  group_by(genre) %>% 
  ggplot(aes(x = platform, fill = platform) ) +
  geom_bar() +
  labs(title = "Games count by Platform") +
  labs(x = "Platform") +
  labs(y = "Number of Games") +
  labs(fill = "Platform") +
  coord_flip()

```


##### 7. Use graph
```{r}
games_sales_full_total_top_200 %>% 
  group_by(genre) %>% 
  ggplot(aes(x = platform, fill = platform) ) +
  geom_bar() +
  theme(legend.position="none") +
  labs(title = "Games count by Platform") +
  labs(x = "Platform") +
  labs(y = "Number of Games") +
  labs(fill = "Platform") +
  coord_flip()
ggsave("platform_count.png")
```


Games by region - global market

```{r}
games_sales_full_longer %>% 
  group_by(genre) %>% 
  ggplot(aes(x = sales_region, y = sales_region_millions) ) +
  geom_line() +
  labs(title = "Geographic breakdown of Global Sales") +
  labs(x = "Specific global market") +
  labs(y = "Sales (millions)") +
  labs(fill = "Genre") +
  coord_flip()

```

```{r}
games_sales_full_total_top_200 %>% 
  group_by(genre) %>% 
  ggplot(aes(x = total_global_sales, fill = genre) ) +
  geom_bar() +
  labs(title = "Geographic breakdown of Global Sales") +
  labs(x = "Sales (millions)") +
  labs(y = "Specific global market") +
  labs(fill = "Genre") +
  coord_flip()

```


### Hide the legend
```{r}
games_sales_full_total_top_200 %>% 
  group_by(genre) %>% 
  ggplot(aes(x = total_global_sales, fill = genre)) +
  geom_bar() +
  theme(legend.position="none") +
  labs(title = "Geographic breakdown of Global Sales") +
  labs(x = "Sales (millions)") +
  labs(y = "Specific global market") +
  labs(fill = "Genre") +
  coord_flip()

```


```{r}
games_sales_full_total_top_200 %>% 
  gather("id", "value", 13:16) %>% 
  ggplot(., aes(total_global_sales, value))+
  geom_point()+
  geom_smooth(method = "lm", se=FALSE, color="black")+
  facet_wrap(~id)
```

```{r}
games_sales_full_longer <- read_csv("games_sales_full_longer.csv")
```



```{r}
games_sales_full_bind_total_longer <- read_csv("games_sales_full_bind_total_longer.csv")
```

```{r}
games_sales_full_bind_total_longer %>%
  group_by(sales_region, year_data) %>%
  summarise(Total = sum(sales_region_millions, na.rm = TRUE))
```




```{r}
games_sales_full_bind_total_longer %>%
  group_by(sales_region, year_data) %>%
  summarise(Total = sum(sales_region_millions, na.rm = TRUE)) %>%
  ggplot(aes(x = sales_region, y = Total)) +
  geom_bar(stat = "identity") +
  labs(title = "Total gobal sales by region") +
  labs(x = "Global market region") +
  labs(y = "Total sales (millions)") +
  facet_wrap(~year_data)

```

```{r}
ggplot(games_sales_full_bind_total_longer, aes(sales_region, total_global_sales)) +
  geom_boxplot() +
  labs(title = "Distribution of sales by genre") +
  labs(x = "Genre") +
  labs(y = "Sales (millions)") +
   coord_flip()
```


##### 8. Use graph


```{r}
games_sales_full_bind_total_longer_region %>%
  ggplot(aes(x = sales_region, y = sales_region_millions)) +
  geom_col() +
  labs(title = "Total gobal sales by region") +
  labs(x = "Global market region") +
  labs(y = "Total sales (millions)") +
  scale_fill_brewer () +
  facet_wrap(~year_data)
```


```{r}
games_sales_full_bind_total<- read_csv("games_sales_full_bind_total.csv")
```


##### Dont use
```{r}
games_sales_full_bind_total_longer %>%
  ggplot(aes(x = sales_region, y = sales_region_millions, fill = genre)) +
  geom_col() +
  labs(title = "Total global sales by region") +
  labs(x = "Total sales") +
  labs(y = "Global market region")
ggsave("sales_region_genre.png")
```


XXXXXXXX WRONG DS
```{r}
games_sales_full_bind_total_longer %>%
  ggplot(aes(x = genre, y = sales_region_millions, fill = sales_region)) +
  geom_col() +
  labs(title = "Total global sales by genre and region") +
  labs(x = "Global market region") +
  labs(y = "Total sales") +
  coord_flip()
ggsave("sales_genre_region.png")
```


####### Correct DS
```{r}
games_sales_full_bind_total_longer %>%
  group_by(sales_region, year_data, genre, sales_region_millions) %>%
  summarise(Total = sum(sales_region_millions, na.rm = TRUE)) %>%
  ggplot(aes(x = genre, y = sales_region_millions, fill = sales_region)) +
  geom_col() +
  labs(title = "Total global sales by genre and region") +
  labs(x = "Global market region") +
  labs(y = "Total sales") +
  coord_flip()
ggsave("sales_genre_region.png")
```




##### 9. Use graph
Games mean (max/ min) sales
```{r}
ggplot(games_sales_full_total_top_200, aes(genre, total_global_sales)) +
  geom_boxplot() +
  labs(title = "Distribution of sales by genre") +
  labs(x = "Genre") +
  labs(y = "Sales (millions)") +
   coord_flip()
ggsave("distribution_sales_by_genre.png")
```

##### 10. Use graph
```{r}
ggplot(games_sales_full_total_top_200, aes(platform, total_global_sales)) +
  geom_boxplot() +
  labs(title = "Distribution of sales by platform") +
  labs(x = "Platform") +
  labs(y = "Sales (millions)") +
   coord_flip()
ggsave("distribution_sales_by_platform.png")
```




shipped / critic score
```{r}

```












