---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(dbplyr)
library(dplyr)
```


```{r}
sales_2016 <- read_csv("sales-2016-with-ratings.csv")
```

```{r}
glimpse(sales_2016)
```

```{r}
head(sales_2016)
```

Look for missing variables and n/a. 
Will need to drop_na()
```{r}
summary(sales_2016)
```


```{r}
names(sales_2016)
```

```{r}
sales_2016_clean <- sales_2016 %>%
  clean_names()
```

```{r}
names(sales_2016_clean)
```


From the information I note:

na_sales = North American sales
eu_sales = European sales
jp_sales = Japan sales
other_sales = rest of world sales
global_sales = sum of all sales

Also year_of_release is character class not an intiger, this will have to be changed.


```{r}
sales_2019 <- read_csv("sales-2019.csv")

```

```{r}
glimpse(sales_2019)
```

```{r}
head(sales_2019)
```


```{r}
names(sales_2019)
```

Look for missing variables and n/a.
Will need to drop_na()
```{r}
summary(sales_2019)
```


```{r}
sales_2019_clean <- sales_2019 %>%
  clean_names()
```

```{r}
names(sales_2019_clean)
```

```{r}
##sales_2019_clean %>% 
  ##ggplot(aes(x = name, y = total_shipped)) +
  ##geom_point()
```

```{r}
##sales_2016_clean %>% 
  ##ggplot(aes(x = name, y = global_sales)) +
  ##geom_point()
```

There are a few outliers (higher sales) in the data

```{r}
sales_2016_clean %>% 
  arrange(desc(global_sales))
sales_2016_clean
```

```{r}
boxplot(sales_2016_clean$global_sales)
```

The outlier is Wii Sports released in 2006

```{r}
view(sales_2016_clean)
```

```{r}
view(sales_2019_clean)
```

```{r}
sales_2019_clean %>% 
  arrange(desc(total_shipped))
sales_2019_clean
```

```{r}
sales_2019_clean %>% 
  arrange(desc(total_shipped))
sales_2019_clean
```

```{r}
boxplot(sales_2019_clean$total_shipped)
```


```{r}
sales_2016_clean %>% 
  select(name, critic_score, global_sales) %>% 
  arrange(desc(critic_score))
```

```{r}
sales_2019_clean %>% 
  select(name, critic_score, total_shipped) %>% 
  arrange(desc(critic_score))
```


```{r}
sales_2016_clean %>% 
  distinct(rating)
```

```{r}
sales_2019_clean %>% 
  distinct(esrb_rating)
```

esrb_rating and rating refer to the esrb_rating categories are the Rating Categories suggest age appropriateness.
E = Everyone
KA = known as Kids to Adults (KA) until 1998, when renamed "Everyone"
EC = Early childhood (years 3+)
E10	= Everyoen over age of 10
T	= Teen
M	= Mature (years 17+)
AO = Adults only (years 18+)		
RP = Rating pending			
				
				
Looking at the vgchartzscore and vg_chartz_score columns.				
```{r}
sales_2019_clean %>% 
  distinct(vgchartzscore)
```			

vg_chartz_score has nothing in any cells
```{r}
sales_2019_clean %>% 
  distinct(vg_chartz_score)
```


```{r}
sales_2019_clean %>% 
  filter(total_shipped > 0) %>% 
  count(global_sales) 
```

```{r}
sales_2019_clean %>% 
  filter(total_shipped > 0) %>% 
  count(na_sales) 
```


```{r}
sales_2019_clean %>% 
  filter(total_shipped > 0) %>% 
  count(pal_sales) 
```

```{r}
sales_2019_clean %>% 
  filter(total_shipped > 0) %>% 
  count(jp_sales) 
```

```{r}
sales_2019_clean %>% 
  filter(total_shipped > 0) %>% 
  count(other_sales)
```

```{r}
sales_2019_clean %>% 
  filter(global_sales > 0) %>%
  select(global_sales, na_sales, pal_sales, jp_sales, other_sales) %>% 
summary
```


```{r}
global_sales_total <- sales_2019_clean %>% 
  filter(global_sales > 0) %>% 
  select(global_sales) %>% 
  sum()
global_sales_total
```


```{r}
na_sales_total <- sales_2019_clean %>% 
  filter(na_sales > 0) %>% 
  select(na_sales) %>% 
  sum()
na_sales_total
```


```{r}
pal_sales_total <- sales_2019_clean %>% 
  filter(pal_sales > 0) %>% 
  select(pal_sales) %>% 
  sum()
pal_sales_total
```


```{r}
jp_sales_total <- sales_2019_clean %>% 
  filter(jp_sales > 0) %>% 
  select(jp_sales) %>% 
  sum()
jp_sales_total
```


```{r}
other_sales_total <- sales_2019_clean %>% 
  filter(other_sales > 0) %>% 
  select(other_sales) %>% 
  sum()
other_sales_total
```

So what is the difference between global sales and all of the ohter regions
```{r}
global_sales_total - (jp_sales_total + na_sales_total + other_sales_total + pal_sales_total)
```


```{r}
sales_2019_clean %>% 
  filter(last_update > 0) %>% 
  distinct(name, last_update) %>%
  arrange(desc(last_update))
```


As the only variable i've not yet looked at
```{r}
sales_2019_clean %>% 
  distinct(status)
```


```{r}
sales_2019_clean %>% 
  filter(vgchartzscore > 0) %>% 
  select(name, critic_score, user_score, vgchartzscore)
```

Which games have 0 sales across all regions (filter by global_sales)
```{r}
sales_2019_clean %>% 
  filter(global_sales == 0) %>% 
  select(name, na_sales, pal_sales, jp_sales, other_sales)
```


```{r}
sales_2019_clean
```

```{r}
sales_2019_clean %>% 
  select(name, platform, global_sales, na_sales, pal_sales, jp_sales, other_sales)

```


Is there more than 1 entry for each game? ie games have entries for each year
There are 37,102 distint rows compared to 55,792 rows in the data set, a difference of 18,690

```{r}
sales_2019_clean %>%
  distinct(name) %>%
  count()
  
```

```{r}
sales_2019_clean %>%
  count(name)

```

There are 61 names with more than 1 entry
```{r}
sales_2019_clean %>%
  count(name > 1) %>%
  arrange()

```


```{r}
sales_2019_clean %>%
  group_by(name, year) %>%
  filter(n() >1) %>%
  count()

```

So there are multiple entries under the same name for each platform eg 2010 FIFA World Cup South Africa
```{r}
sales_2019_clean %>%
  filter(name == "2010 FIFA World Cup South Africa")

```

```{r}
sales_2019_clean %>%
  filter(name == "007: Quantum of Solace")

```

```{r}
sales_2019_clean %>%
  filter(name == "007: Quantum of Solace") %>%
  ggplot(aes(x = platform, y = total_shipped)) +
  geom_point()

```

There looks to be a difference between sales for example for 007: Quantum of Solace across platforms, so lets have a look at all platforms

```{r}
sales_2019_clean %>% 
  filter(total_shipped != 0) %>%
  ggplot(aes(x = platform, y = total_shipped)) +
  geom_point()
```

```{r}
sales_2019_clean %>% 
  filter(total_shipped >10) %>%
  ggplot(aes(x = platform, y = total_shipped)) +
  geom_point()
```

Lets count by platform

```{r}
sales_2019_clean %>%
  group_by(platform) %>%
  filter(n() > 1) %>%
  arrange(n()) %>%
  count()

```

```{r}
sales_2019_clean %>%
  group_by(platform) %>%
  arrange(n()) %>%
  count()

```



```{r}
sales_2019_clean %>%
  group_by(platform) %>%
  count()

```

```{r}
sales_2019_clean_platform <- sales_2019_clean %>%
  group_by(platform) %>%
  mutate("platform_sales" = n())
sales_2019_clean_platform

```

```{r}
sales_2019_clean_platform %>%
  count() %>%
  arrange(desc(n))
```
 
Now lets have a look at Genre in the dataset 

```{r}
sales_2019_clean %>% 
  filter(total_shipped >10) %>%
  ggplot(aes(x = genre, y = total_shipped)) +
  geom_point()

```

```{r}
sales_2019_clean %>%
  group_by(genre) %>%
  count()

```

Also whatis the best publisher?
```{r}
sales_2019_clean %>% 
  filter(total_shipped > 5) %>%
  ggplot(aes(x = total_shipped, y = publisher)) +
  geom_point()

```

Lets look at critic_score
```{r}
sales_2019_clean %>% 
  filter(critic_score > 9.5) %>%
  ggplot(aes(x = critic_score, y = name)) +
  geom_point()

```

Summary of findings and comparision between the 2 datasets 1. sales_2016 and 2. sales_2019

2 datasets 2016 and 2019

2016
 
"Critic_Count" 
"User_Count"

2019       v        2016
"Rank"              = n/a
[1] "Name"          = "Name"
"basename"          = n/a (games names )
"Genre"             =   "Genre"
"ESRB_Rating"       = "Rating" As above this rating references if games are age appropriate
"Platform"          = "Platform"
"Publisher"         = "Publisher"
"Developer"         = "Developer"
"vg_chartz_score"   = n/a (also contains no variables)
[9] "VGChartz_Score"= n/a
"Critic_Score"      = "Critic_Score" (2016 and 2019 are scored differently. From 100 in 2016 and from 10 in 2019)
"User_Score"        = [13] "User_Score"
"Total_Shipped"     = n/a
"Global_Sales"      = "Global_Sales"
"NA_Sales"          =  "NA_Sales"  
"PAL_Sales"        != [7] "EU_Sales" (PAL usually refers to Asia, Africa, Europe, South America and Oceania) SO these dont natch
"JP_Sales"          =  "JP_Sales"
[17] "Other_Sales"  =  "Other_Sales"
"Year"              =  "Year_of_Release"
"Last_Update"       = n/a
"url"               = n/a
"status"            = n/a. No variables in 
"Vgchartzscore"     = n/a
"img_url"           = n/a


Convert years to Intiger
```{r}
###sales_2016_clean <- sales_2016_clean %>% 
  #mutate(
    #year_of_release = as.integer(year_of_release))
#sales_2016_clean
```


```{r}
###sales_2019_clean <- sales_2019_clean %>% 
  #mutate(
   # year = as.integer(year))
#sales_2019_clean
```

```{r}
#### sales_2019_clean <- sales_2019_clean %>% 
  #mutate(
   # year = as.integer(year))
#sales_2019_clean
```


1. I will fill in missing sales volumes
2. Exclude basename from 2019 results
3. Change critic_score in 2016 to critic_score_2016 and do the same for 2019
4. change pal_sales in 2019 to eu_sales_2019 and add the year to 

```{r}
sales_clean_2019_select_var <- sales_2019_clean %>% 
  select(-basename,
  -vg_chartz_score,
  -url,
  -status,
  -img_url)
sales_clean_2019_select_var
```

I still need to look at and possibly remove the NA's

Lets amend the dates in for sales to 2019
```{r}
sales_clean_2019_year <- sales_clean_2019_select_var %>% 
  rename(
    "total_shipped_2019" = "total_shipped",
    "global_sales_2019" = "global_sales",
    "na_sales_2019" = "na_sales",
    "eu_sales_2019" = "pal_sales",
    "jp_sales_2019" = "jp_sales",
    "other_sales_2019" = "other_sales")
sales_clean_2019_year
```

```{r}
view(sales_clean_2019_year)
```

Now lets do the same for 2016

```{r}
sales_2016_clean_select <- sales_2016_clean %>% 
  select(-year_of_release,
  -critic_count,
  -user_count,
  -user_score,
  -rating)
sales_2016_clean_select 
```

```{r}
sales_clean_2016_year <- sales_2016_clean_select %>% 
  rename(
    "na_sales_2016" = "na_sales",
    "eu_sales_2016" = "eu_sales",
    "jp_sales_2016" = "jp_sales",
    "other_sales_2016" = "other_sales",
    "global_sales_2016" = "global_sales")
sales_clean_2016_year
```


```{r}
sales_clean_2019_select_var_bind <- sales_clean_2019_select_var %>%
  rename(
  "eu_sales" = "pal_sales"
  )
sales_clean_2019_select_var_bind
```


##### Bind columns

```{r}
sales_2016_clean_select_bind <- sales_2016_clean_select %>%
  mutate(year_data = 2016)

sales_2019_clean_select_bind <- sales_clean_2019_select_var_bind %>%
  mutate(year_data = 2019)

games_sales_full_bind <- bind_rows(sales_2016_clean_select_bind, sales_2019_clean_select_bind)
games_sales_full_bind
```

```{r}
unique(games_sales_full_bind$year_data)
```

```{r}
games_sales_full_bind_select <- games_sales_full_bind %>% 
  select(
  -user_score)
games_sales_full_bind_select 
```


```{r}
names(sales_2016_clean)
```

```{r}
names(sales_2019_clean)
```

########
```{r}
games_sales_full_bind_total <- mutate(games_sales_full_bind, total_global_sales = total_shipped + global_sales)
games_sales_full_bind_total
```




```{r}
games_sales_full_bind_total %>%
  arrange(total_global_sales)
games_sales_full_bind_total
```

```{r}
summary(games_sales_full_bind_total)
```


```{r}
write.csv(games_sales_full_bind_total, "games_sales_full_bind_total.csv")
```

```{r}
games_sales_full_bind_total_longer <- games_sales_full_bind_total %>% 
  pivot_longer(cols = c("na_sales", "eu_sales", "jp_sales", "other_sales"),
               names_to = "sales_region",
               values_to = "sales_region_millions")
games_sales_full_bind_total_longer
```

```{r}
games_sales_full_bind_total_longer %>%
  filter(sales_region == "na_sales") %>%
  summarise(Total = sum(sales_region_millions, na.rm = TRUE))
```

```{r}
games_sales_full_bind_total_longer %>%
  group_by(sales_region, year_data) %>%
  summarise(Total = sum(sales_region_millions, na.rm = TRUE))
```


```{r}
write.csv(games_sales_full_bind_total_longer, "games_sales_full_bind_total_longer.csv")
```









I also need to amend pal_sales to eu_sales

```{r}
games_sales_full <- left_join(sales_clean_2019_year, sales_clean_2016_year)
games_sales_full
```


```{r}
dim(games_sales_full)
```


```{r}
view(games_sales_full)
```

```{r}
summary(games_sales_full)
```


#################

Replace NA with 0


```{r}
games_sales_full_na <- games_sales_full %>%
    mutate(total_shipped_2019 = replace(total_shipped_2019, 
                                    is.na(total_shipped_2019), 0
                                   )) %>%
  mutate(global_sales_2019 = replace(global_sales_2019, 
                                    is.na(global_sales_2019), 0
                                   )) %>%
  mutate(global_sales_2016 = replace(global_sales_2016, 
                                    is.na(global_sales_2016), 0
                                   ))
games_sales_full_na
```


```{r}
games_sales_full_total <- mutate(games_sales_full_na, total_global_sales = total_shipped_2019 + global_sales_2019 + global_sales_2016)
games_sales_full_total
```



```{r}
games_sales_full_total %>%
  arrange(games_sales_full_total)
games_sales_full_total
```


```{r}
view(games_sales_full_total)
```


```{r}
write.csv(games_sales_full_total, "games_sales_full_total_cleaned.csv")
```

```{r}
games_sales_full_longer <- games_sales_full_total %>% 
  pivot_longer(cols = c("global_sales_2019", "na_sales_2019", "eu_sales_2019", "jp_sales_2019", "other_sales_2019"),
               names_to = "sales_region",
               values_to = "sales_region_millions")
games_sales_full_longer
```



```{r}
write.csv(games_sales_full_longer, "games_sales_full_longer.csv")
```

 

